Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-29 dit-paper_ieee.tex
- size ratio discussion

	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets without
	synchronous instants were generated and the size of their C-space was
	calculated and compared with the size of the C-space of the same
	task sets with all task offsets set to zero. In other words, this figure
	evaluates the feasibility gain of adding random offsets to a synchronous task
	set. It is assumed that a more advanced strategy to assign these offsets
	would yield a greater difference.

@@

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
% \nocite{*}
\bibliographystyle{plain}
\bibliography{dit-paper}

>>>>

	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets of
	three tasks without synchronous instants were generated. The size of their
	C-space was calculated and compared with the size of the C-space of the same
	task sets with all task offsets set to zero. In other words, this figure
	evaluates the feasibility gain of adding random offsets to a synchronous task
	set. It is assumed that a more advanced strategy to assign these offsets
	would yield a greater difference.

@@

	The ratio between the size of the synchronous and asynchronous C-spaces of
	these systems roughly range from 0.95 in the worst case (high utilization, high
	CDF) to 0.85 in the best case (low utilization, low CDF). Note that the value
	of the CDF has a greater influence on this ratio than the system's total
	utilization, but less so when the CDF is lower. It is also important to note
	that even though a 0.95 ratio may not seem much, the synchronous C-spaces of
	the systems contain many dominated WCET vectors, and only those that are
	pareto-optimal (i.e. non-dominated) actually matter to the system's engineer.
	Using the asynchronous C-space instead will relax some constraints and therefore add new acceptable
	solutions that will dominate solutions that were previous non-dominated,
	increasing the quality of the WCET pareto-front.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
% \nocite{*}
\bibliographystyle{IEEEtran}
\bibliography{dit-paper}
